---
title: "P8105 Homework 6"
author: "Laylah Jones"
date: 2023-12-02
output: github_document
---

```{r, include=FALSE, message = FALSE, warning = FALSE}
library(tidyverse)
library(ggplot2)
library(purrr)
library(modelr)


options(readr.show_col_types = FALSE)

knitr::opts_chunk$set(
  fig.width = 8,
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = ("viridis"))

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Problem 1


# Problem 2

### Loading the Data

```{r, load}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2022-01-01",
    date_max = "2022-12-31") |>
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())
```

### Creating Bootstrap and Getting Estimates

```{r}
boot_sample = function(df) {
  sample_frac(df, replace = TRUE)
}
```

```{r}
set.seed(1)

boot_strap = 
  tibble(strap_number = 1:5000) |> 
  mutate(
    strap_sample = map(strap_number, \(i) boot_sample(weather_df))
  )
```

```{r, lm}
boot_results = 
  boot_strap |> 
  mutate(
    models = map(strap_sample, \(df) lm(tmax ~ tmin + prcp, data = df)),
    tidy_results = map(models, broom::tidy),
    glance_results = map(models, broom::glance)
  ) |> 
  select(strap_number, tidy_results, glance_results) |> 
  unnest(tidy_results, glance_results)
```

```{r}
logb1b2_results = boot_results |> 
  select(strap_number, term, estimate, std.error) |> 
  filter(term %in% c("tmin","prcp")) |> 
  pivot_wider(
     names_from = term,
     values_from = c(estimate, std.error)
  ) |> 
  mutate(
    logb1b2 = log(estimate_tmin * estimate_prcp)
  ) 

rsq_results = boot_results |> 
  select(strap_number, r.squared) |> 
  distinct(.keep_all = TRUE)
```

### Plotting Distribution of Estimates

```{r, plot}
logb1b2_results |> 
  ggplot(aes(x = logb1b2)) + 
  geom_density() +
  labs(
    title = "Estimation of log(b1*b2)")

rsq_results |> 
  ggplot(aes(x = r.squared)) + 
  geom_density() + 
  labs(
    title = "Esimation of R squared")
```

The distribution of ${r^2}$ is normal, with it being centered around 0.920. It shows a visibly heavy tail extending to low values, and a bump which could be attributed to the occurrence of large outliers withing the bootstrap samples.

The distribution of log($\hat{beta_1} * \hat{beta_2}$) is uni-modal and left-skewed. Due to negative precipitation values, and we can see this distribution after we remove the NA values. The distribution shows an even more visibly heavy tail extending to the low values, with majority of the values clustering on the right side.

### 95% CI for log(b1*b2)

```{r, CI}
logb1b2_results |> 
  summarise(
  upperCI = quantile(logb1b2, 0.975, na.rm = TRUE),
  lowerCI = quantile(logb1b2, 0.025, na.rm = TRUE)) |> 
  knitr::kable()
```

This is the 95% confidence interval for log($\hat{beta_1} * \hat{beta_2}$) after removing the NA values.

### 95% CI for R-Squared

```{r, CI_R}
rsq_results |> 
  summarise(
  upperCI = quantile(r.squared, 0.975, na.rm = TRUE),
  lowerCI = quantile(r.squared, 0.025, na.rm = TRUE)) |> 
  knitr::kable()
```


# Problem 3

### Loading and Cleaning the data

```{r}
birthweight_df = 
  read_csv("data/birthweight.csv") |> 
  janitor::clean_names() |> 
  mutate(
    babysex = as.factor(babysex),
    babysex = recode(babysex, "1" = "Male", "2" = "Female"),
    frace = as.factor(frace),
    frace = recode(frace, "1" = "White", "2" = "Black", "3" = "Asian", "4" = "Puerto Rican", "8" = "Other", "9" = "Unknown"),
    malform = as.factor(malform),
    malform = recode(malform, "0" = "Absent", "1" = "Present"),
    mrace = as.factor(mrace),
    mrace = recode(mrace, "1" = "White", "2" = "Black", "3" = "Asian", "4" = "Puerto Rican", "8" = "Other")
  )

head(birthweight_df)

purrr::map(birthweight_df, ~sum(is.na(.)))
```

### Making the Regression Model

```{r}
model_1 = lm(bwt ~ babysex + fincome + gaweeks + malform + smoken + wtgain, data = birthweight_df)

model_1
```

My regression model consists of the variables `babysex`, `fincome`, `gaweeks`, `malform`, `smoken`, and `wtgain`. From this, I hypothesize that these specific variables underly birthweight.

### Plot of Regression Model

```{r}
birthweight_plot =
birthweight_df |> 
  modelr::add_predictions(model_1) |>  
  modelr::add_residuals(model_1) |>  
  ggplot(aes(x = pred, y = resid)) +
  geom_point(alpha = .2) +
  labs(
    x = "Fitted Values",
    y = "Residuals",
    title = "Residuals vs Fitted Values"
  )

birthweight_plot
```

### Cross Validation

```{r}
set.seed(1)

cross_validation = 
  crossv_mc(birthweight_df, 100) |>
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)) |> 
  mutate(
    model_1 = map(.x = train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    model_2 = map(.x = train, ~lm(bwt ~ bhead * blength * babysex, data = .x)),
    my_model = map(.x = train, ~lm(bwt ~ babysex + fincome + gaweeks + malform + smoken + wtgain, data = .x))
  ) |> 
  mutate(
    rmse_model_1 = map2_dbl(.x = model_1, .y = test, ~rmse(model = .x, data = .y)),
    rmse_model_2 = map2_dbl(.x = model_2, .y = test, ~rmse(model = .x, data = .y)),
    rmse_my_model = map2_dbl(.x = my_model, .y = test, ~rmse(model = .x, data = .y))
  )

cross_validation

cross_validation_plot =
 cross_validation |>  
  select(starts_with("rmse")) |>  
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) |>  
  mutate(
    model = recode(model, "model_1" = "Model 1", "model_2" = "Model 2", "my_model" = "My Model")
  ) |>  
  ggplot(aes(
    x = model, 
    y = rmse)) +
  geom_violin() +
  labs(
    x = "Model",
    y = "RMSE",
    title = "RMSE by Model"
  )

cross_validation_plot
```

